---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

First, I'm just going to load the data and leave it as is for now.

```{r echo=TRUE}
actvt <- read.csv("activity.csv")
```

We loaded `r nrow(actvt)` rows. 


## What is mean total number of steps taken per day?

I'm creating a sum aggregate of steps by day.
```{r echo=TRUE}
by_day <- aggregate(actvt$steps, list(date=actvt$date), sum)
```

### Histogram
And then I'm displaying it as histogram.
```{r echo=TRUE}
hist(by_day$x, breaks=23, main="Daily Steps", xlab="Steps")
```

### Mean & Median
```{r}
steps_mean <- round(mean(by_day$x, na.rm=TRUE),2)
steps_median <- median(by_day$x, na.rm=TRUE)
print(paste("mean steps per day: ", steps_mean))
print(paste("median steps per day: ", steps_median ))
```


## What is the average daily activity pattern?

I'm aggregating using the mean per interval and then plotting.
```{r echo=TRUE}
interval_steps = aggregate(actvt$steps, list(as.factor(actvt$interval)), mean, na.rm=TRUE)
plot(interval_steps, type="l", ylab="Average steps", xlab="Interval")
```

Find the interval with the highest average steps
```{r}
h_interval <- interval_steps[which.max(interval_steps$x),]
```

The interval with the highest number of steps is `r as.numeric(as.character(h_interval$Group.1))` with an average of `r round(h_interval$x,2)`


## Imputing missing values

### Find rows with missing values:
```{r}
missing <- nrow(actvt[which(is.na(actvt$steps)),])
```

There are `r missing` rows with missing values.

I'm going to assign to each missing value the mean for that interval. I can rely on the `interval_steps` aggregate I created earlier.

I'll iterate over the missing values setting them to the corresponding mean from interval steps then create a new variable called `actvt_filled`.

```{r}

```


## Are there differences in activity patterns between weekdays and weekends?
